Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-09-05 parts/massmodel.tex

Fig.~\ref{fig:kappa} shows the projected mass maps of the sample.  In
fact, this figure only shows the ensemble-average mass maps, and not
the variation within the ensemble, from which uncertainties can be
inferred. The same applies to the arrival-time surfaces and synthetic
images in the previous two figures. The uncertainties will be shown in
a concise form in Fig.~\ref{fig:encl}.  Fig.~\ref{fig:kappa} makes
evident the tiled nature of the mass model.  The tiles can be smoothed
over by interpolation, and this was done in the mass maps during the
modelling process, available in the online version.  It is
interesting, however, to note the tiling artifacts, if only as a
reminder that the substructure in the mass distribution is very
uncertain, even if some integrated quantities are  well
constrained.  How the free-form mass maps relate to parameterised lens
models is discussed in Appendix~\ref{subsec:parameter}.
\textcolor{red}{{\bf IF: This sentence is confusing and needs some
    clarification:} Note that the arrival-time surface does not have
  discontinuous jumps, because the modelling numerics uses an
  analytical integral over square tiles; likewise the lens equation.}

>>>>

Fig.~\ref{fig:kappa} shows the projected mass maps of the sample.  In
fact, this figure only shows the ensemble-average mass maps, and not
the variation within the ensemble, from which uncertainties can be
inferred. The same applies to the arrival-time surfaces and synthetic
images in the previous two figures. The uncertainties will be shown in
a concise form in Fig.~\ref{fig:encl}.  Fig.~\ref{fig:kappa} makes
evident the tiled nature of the mass model.  The tiles can be smoothed
over by interpolation, and this was done in the mass maps during the
modelling process, available in the online version.  It is
interesting, however, to note the tiling artifacts, if only as a
reminder that the substructure in the mass distribution is very
uncertain, even if some integrated quantities are  well
constrained.  How the free-form mass maps relate to parameterised lens
models is discussed in Appendix~\ref{subsec:parameter}.
Note that although the mass distribution can have discontinuous jumps,
the lens equation and arrival-time surface are continuous.
